PANCHANGE_analysis

### 2020-08-25 PANCHANGE_analysis.Rmd
added covid positive single and double

@@

# COVID
## COVID swab test positive
```{r COVID positive swap}
dat %>%
  count(respiratory.throat_swab_test_nose, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

@@

>>>>

# Positive covid test results
```{r}

@@

# COVID
## Recode variable
```{r gad covid test positive double}
dat <- dat %>%
  mutate(gad.covid_test_positive_double_numeric =
           case_when(
             (respiratory.throat_swab_test_nose_numeric == 1 &
               respiratory.results_antibody_test_numeric == 1) ~ 2,
             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
             respiratory.results_antibody_test_numeric == 1 ~ 1,
             respiratory.results_antibody_test_numeric == 2 ~ 0
           )
         )

dat <- dat %>%
  mutate(covid_test_positive_double =
           recode_factor(
             gad.covid_test_positive_double_numeric,
             `0` = "Negative",
             `1` = "Positive",
             `2` = "Double positive"
           )
         )

dat %>%
  freq(covid_test_positive_double)
```

```{r gad covid test positive}
dat <- dat %>%
  mutate(gad.covid_test_positive_numeric =
           case_when(
             (respiratory.throat_swab_test_nose_numeric == 1 &
               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
             respiratory.results_antibody_test_numeric == 1 ~ 1,
             respiratory.results_antibody_test_numeric == 2 ~ 0
           )
         )

dat <- dat %>%
  mutate(covid_test_positive =
           recode_factor(
             gad.covid_test_positive_numeric,
             `0` = "Negative",
             `1` = "Positive"
#             `2` = "Double positive"
           )
         )

dat %>%
  freq(covid_test_positive)
```

## COVID swab test positive
```{r COVID positive swap}
dat %>%
  count(respiratory.throat_swab_test_nose, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

@@

## Cross table probable covid and covid test positive
```{r}
dat %>%
```
